### 2022-05-06 manuscript.Rmd
Add contours and gender analysis to funnel plot

```{r, fig3, include=TRUE, fig.height=3.5, fig.width=5.56, fig.cap="(ref:fig3-caption)", out.width="50%"}
# Compute funnel
funnel_z_crit <- stats::qnorm(0.975)
funnel_max_se <- 0.5 # A bit larger than the largest observed `sei` in `dat`
funnel_tau2 <- 0 # We don't take heterogeneity into account, only the SE
funnel <- data.frame(
  x = c(
    summ_brm$intercept - funnel_z_crit * sqrt(funnel_max_se^2 + funnel_tau2),
    summ_brm$intercept - funnel_z_crit * sqrt(funnel_tau2),
    summ_brm$intercept + funnel_z_crit * sqrt(funnel_tau2),
    summ_brm$intercept + funnel_z_crit * sqrt(funnel_max_se^2 + funnel_tau2)
  ),
  y = c(funnel_max_se, 0, 0, funnel_max_se)
)

# Create funnel plot
dat %>%
  ggplot(aes(x = gi, y = sei)) +
  geom_vline(xintercept = seq(-2, 2, 0.5), color = "grey90") +
  # Meta-analytic effect size
  geom_vline(xintercept = summ_brm$intercept, color = "black") +
  # Experiment-specific effect sizes
  geom_point(shape = 0) +
  # Funnel
  geom_path(data = funnel, aes(x = x, y = y), linetype = "dashed") +
  # Styling
  scale_x_continuous(breaks = seq(-2, 2, 0.5)) +
  scale_y_reverse() +
  coord_cartesian(
    xlim = c(-2.5, 2.5),
    ylim = c(funnel_max_se, 0),
    expand = FALSE
  ) +
  labs(
    x = expression("Hedges'" ~ italic("g")),
    y = "Standard error",
  ) +
  theme_classic() +
  theme(
    axis.line = element_line(colour = "black"),
    axis.text = element_text(family = "Helvetica", color = "black"),
    axis.ticks = element_line(color = "black"),
    text = element_text(family = "Helvetica", color = "black")
  )

# Save the plot
ggsave(here(figures_dir, "funnel.pdf"), width = 5.56, height = 3.5)
```

>>>>

```{r, fig3, include=TRUE, fig.height=3.5, fig.width=12, fig.cap="(ref:fig3-caption)"}
# Create funnel plots
list(dat, dat_gender) %>%
  map(function(plot_dat) {

    # Define maximul SE of interest (a bit larger than the largest observed one)
    max_se <- max(plot_dat$sei) + 0.05

    # Compute two different funnels under the null hypothesis
    z_crit_05 <- stats::qnorm(0.975)
    funnel_05 <- data.frame(
      x = c(0 - z_crit_05 * sqrt(max_se^2), 0, 0 + z_crit_05 * sqrt(max_se^2)),
      y = c(max_se, 0, max_se)
    )

    # Compute two different funnels under the null hypothesis
    z_crit_01 <- stats::qnorm(0.995)
    funnel_01 <- data.frame(
      x = c(0 - z_crit_01 * sqrt(max_se^2), 0, 0 + z_crit_01 * sqrt(max_se^2)),
      y = c(max_se, 0, max_se)
    )

    # Compute funnel around the observed meta-analytic effect size
    funnel_observed <- mutate(funnel_05, x = x + summ_brm$intercept)

    # Plot the funnel(s)
    ggplot(plot_dat, aes(x = gi, y = sei)) +
      # Null funnels
      geom_polygon(
        data = funnel_01, aes(x = x, y = y), fill = "grey60", alpha = 0.2
      ) +
      geom_polygon(
        data = funnel_05, aes(x = x, y = y), fill = "grey60", alpha = 0.2
      ) +
      # Grid lines
      geom_vline(xintercept = seq(-2, 2, 0.5), color = "grey90") +
      # Observed_funnel
      geom_path(data = funnel_observed, aes(x = x, y = y)) +
      # Meta-analytic effect size
      geom_vline(xintercept = summ_brm$intercept, color = "black") +
      # Experiment-specific effect sizes
      geom_point(shape = 0) +
      # Styling
      scale_x_continuous(breaks = seq(-2, 2, 0.5)) +
      scale_y_reverse() +
      coord_cartesian(
        xlim = c(-2.5, 2.5),
        ylim = c(max_se, 0),
        expand = FALSE
      ) +
      labs(
        x = expression("Hedges'" ~ italic("g")),
        y = "Standard error",
      ) +
      theme_classic() +
      theme(
        axis.line = element_line(colour = "black"),
        axis.text = element_text(family = "Helvetica", color = "black"),
        axis.ticks = element_line(color = "black"),
        text = element_text(family = "Helvetica", color = "black")
      )
  }) %>%
  plot_grid(
    plotlist = ., nrow = 1, labels = "auto",
    label_size = 11, label_fontfamily = "Helvetica"
  )

# Save the plot
ggsave(here(figures_dir, "funnel.pdf"), width = 12, height = 3.5)
```
